\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}

\title{Chinook Music Store: Revenue Snapshot 2021--2025}
\author{Orchid Sample Workspace}
\date{\today}

\begin{document}
\maketitle

\begin{abstract}
This snapshot summarizes sales for the Chinook sample music store over the period
2021--2025. Across the full window the store recorded \$2{,}328.60 in revenue from
412 invoices. Revenue is concentrated by genre: Rock alone accounts for 35.5\% of the
total, and the top four genres together make up 73.5\% of all sales. Customer value is
comparatively even, with the ten largest customers contributing under one fifth of revenue.
\end{abstract}

\section{Overview}
The Chinook dataset models a digital music store: artists, albums, tracks, customers, and
invoices. Over 2021--2025 the store's revenue was essentially flat year to year, so the
useful structure lives in the \emph{mix} of what sold rather than in any growth trend. The
sections below break revenue down by genre and then by customer.

\section{Revenue by Genre}
Table~\ref{tab:genre} lists the ten highest-grossing genres by total revenue, with the number
of individual tracks sold in each. Rock leads by a wide margin, and the top four genres
(Rock, Latin, Metal, and Alternative \& Punk) account for 73.5\% of revenue between them.

\begin{table}[h]
\centering
\begin{tabular}{lrr}
\hline
\textbf{Genre} & \textbf{Revenue (\$)} & \textbf{Tracks sold} \\
\hline
Rock & 826.65 & 835 \\
Latin & 382.14 & 386 \\
Metal & 261.36 & 264 \\
Alternative \& Punk & 241.56 & 244 \\
TV Shows & 93.53 & 47 \\
Jazz & 79.2 & 80 \\
Blues & 60.39 & 61 \\
Drama & 57.71 & 29 \\
R\&B/Soul & 40.59 & 41 \\
Classical & 40.59 & 41 \\
\hline
\end{tabular}
\caption{Top ten genres by revenue, 2021--2025.}
\label{tab:genre}
\end{table}

\section{Customers}
Customer spending is remarkably even across the base. The ten highest-value customers together
account for just 19.4\% of total revenue, and individual lifetime value falls within a narrow
\$36.64--\$49.62 band. There is little concentration to exploit and, because nearly every
customer placed the same number of orders, little churn signal to model.

\section{Next Steps}
Natural extensions of this snapshot include a country-level revenue breakdown, a per-artist
catalog contribution analysis, and a cohort view of invoices by month. Each can be built
directly on the bundled Chinook SQLite integration from within Orchid.

\end{document}
